Unitary evolution as a quasistatic process of infinitesimal collapses

### 2019-04-02 Articles/2019-ForQuantumOptics/article.tex
Minor change

Violations of the Schroedinger equation, then, should be expected only for processes that cannot be considered quasistatic. If we were to implement a measurement process, then, in a way that the transfer of information between the system and the probe happens in a slow and controlled fashion, this could not provide a violation of the Schroedinger equation, nor would it tell us that all projections are quasistatic processes. A better description of the faster scale processes given by the projections, then, will inevitably need a new state space as the standard quantum states only describe equilibria, and we should expect the faster scale processes to go out of equilibrium. Ultimately, a description at Plank time scale will fail to be continuous and quasistatic since a finite change in a finite time will not be divided into infinitesimal adiabatic changes over infinitely many time steps.

>>>>

Violations of the Schroedinger equation, then, should be expected only for processes that cannot be considered quasistatic. If we were to implement a measurement process, then, in a way that the transfer of information between the system and the probe happens in a slow and controlled fashion, this could not provide a violation of the Schroedinger equation, nor would it tell us that all projections are quasistatic processes. A better description of the faster scale processes given by the projections, then, will inevitably need a new state space as the standard quantum states only describe equilibria, and we should expect the faster scale processes to go out of equilibrium. Consequently, a description at Planck time scale will ultimately fail to be continuous and quasistatic since a finite change in a finite time will not be divided into infinitesimal adiabatic changes over infinitely many time steps.
